Measuring efficiency of the greedy-like heuristics for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization

### 2020-10-07 doc/paper.tex

	\subsection{Discretization}
	The discretization $D(P)$ of the polygon $P$ is built as follows. Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of polygon $P$ which height and weight are defined as follow:
	\begin{equation}
         \bigtriangleup_{x}=\min\{ |u_{x}-v_{x}|\mid u_{x}\neq v_{x}\} \mbox{ and }
         \bigtriangleup_{y}=\min\{ |u_{y}-v_{y}|\mid u_{y}\neq v_{y}\},
 	\end{equation}
where $ (u_{x},u_{y}),(v_{x},v_{y})$ are adjacent vertices of polygon $P$.

@@

	\section{Exact methods}
	In this section we present the exact ILP and \emph{Constraint Programming} (CP) models for solving WMSCP, which are used  in the rest of the paper.
	\subsection{Integer linear programming model}
	Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.  The task we consider is covering all points from $D(P)$ by some vertices $V=\{v_1,...,v_n\}$ of $P$ such that the sum of their weights is minimized.
	The problem is related to the known MWSC problem.
	Family $\mathcal{F}$ of nonempty sets consists of sets
	$S_i \in \mathcal{F}$ which include point $p \in D(P)$ that is visible from guard $v_i\in V$, that is $pv_i \subset P$.  Note that set $S_i$ includes a point $p_i$ which can also included by some other guard $v_j\in V$, $i \neq j$. To each set set $S_i$, a cost $c(S_i) = w_i$ is assigned.  In this way, our starting task is then equivalent of finding a minimum cardinalty cover $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
	$$ \bigcup_{C \in \mathcal{C}} C = D(P)$$ such that $\sum_{S_i \in \mathcal{C}} c(S_i)$ is minimized.  The ILP  model for the WSCP is known from the literature, and is here adapted to WOAGP  as follows:
	\begin{align}
	&\sum_{i=1}^n w_ix_i \longrightarrow \min \\
	&\mbox{s.t.} \\
	&\sum_{j\in V} a_{ij}x_j \geq 1\ (\forall p_i\in D(P)) \label{eq:const-3}\\
	& x_j \in \{0,1\}, j \in V,
	\end{align}
	where
	$a_{ij} = \begin{cases}
	1, p_i \in V(j), \\
	0, \mbox{otherwise}
	\end{cases}$
	and $x_i = \begin{cases}
	1, \mbox{ if } \mbox{ the point } p_i \in \mathcal{C},\\
	0, \mbox{otherwise},
	\end{cases}$ \\
	where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
	Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
	Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.

	In order to solve this model, we apply a general purpose solver \textsc{Cplex}~\cite{lima2010ibm}.
	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by ILOG IBM CP Optimizer~\cite{}. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
	\begin{equation}
	\bigvee_{ j \in V } (a_{ij} \wedge x_j) = 1,
	\end{equation}
	whereas the other constraints and the objective function are the same like in the above MIP model. Note that CP appraoch works in a branch-and-bound manner imploying a constriant propagation and variable domain filtering~\cite{laborie2018ibm}.
	\section{Algorithmic Approaches for WOAGP}
	\subsection{Greedy approaches for solving WOAGP}
	Since the WOAGP instances can be transformed into  WMSCP instances and since one of the most efficient heuristics to solve WSCP from the literature is an enhanced greedy heuristic~\cite{chvatal1979greedy}, our idea is after transforming a WOAGP instance into a WSC problem instance to	apply various greedy algorithms to solve WOAGP. Greedy algorithms produce a solution of reasonable quality within a short interval of time and are, in essence, easy to implement. Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one. Among all candidates (solution components for expansion, that is not-yet-considered guards) we choose one with the smallest greedy value and add it to the current solution until it is complete (i.e., it covers all  points from $D(P)$).
	A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}

>>>>

	\subsection{The Regular Discretization of Polygon}  
	The discretization $D(P)$ of the polygon $P$ is built as follows. Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of polygon $P$ which height and weight are defined as follow:

	\begin{equation}
         \bigtriangleup_{x}=\min\{ |u_{x}-v_{x}|\mid u_{x}\neq v_{x}\} \mbox{ and }
         \bigtriangleup_{y}=\min\{ |u_{y}-v_{y}|\mid u_{y}\neq v_{y}\},
 	\end{equation}
where $ (u_{x},u_{y}),(v_{x},v_{y})$ are adjacent vertices of polygon $P$.

@@

	\section{Exact methods}
	In this section we present the exact ILP and \emph{Constraint Programming} (CP) models for solving WMSCP  under regular grid discretization, which are used  in the rest of the paper.
	\subsection{Integer linear programming model}
	Let us suppose we are given a polygon $P$ and a discretization $D(P)$ of $P$.  The task we consider is covering all points from $D(P)$ by some vertices $V=\{v_1,...,v_n\}$ of $P$ such that the sum of their weights is minimized.
	The problem is related to the known MWSC problem.
	Family $\mathcal{F}$ of nonempty sets consists of the sets
	$S_i \in \mathcal{F}$ which include points $p \in D(P)$ that are visible from guard $v_i\in V$, i.e., $pv_i \subset P$.  Note that set $S_i$ includes points $p\in D(P)$ that might also be included by some other guard $v_j\in V$, $i \neq j$. For each set $S_i$, the cost $c(S_i) = w_i$ is assigned.  In this way, our starting task is equivalent of finding a minimum cardinalty covering $\mathcal{C}\subseteq\{S_1,...,S_n\}$ of the set of points $D(P)$, that is
	$$ \bigcup_{C \in \mathcal{C}} C = D(P),$$ such that $\sum_{S_i \in \mathcal{C}} c(S_i)$ is minimized.  The ILP  model for the WSCP is already known from the literature, where  here adapted to WOAGP  as follows:

	\begin{align}
	&\sum_{i=1}^n w_ix_i \longrightarrow \min \\
	&\mbox{s.t.} \\
	&\sum_{j\in V} a_{ij}x_j \geq 1\ (\forall p_i\in D(P)) \label{eq:const-3}\\
	& x_j \in \{0,1\}, j \in V,
	\end{align}
	where
	$a_{ij} = \begin{cases}
	1, p_i \in V(j), \\
	0, \mbox{otherwise}
	\end{cases}$
	and $x_i = \begin{cases}
	1, \mbox{ if } \mbox{ the point } p_i \in \mathcal{C},\\
	0, \mbox{otherwise},
	\end{cases}$ \\

	where $V(j)$ is the set of all points from $D(P)$ that are visible from $j$-th vertex of $P$.
	Set $Z = \{j \in V\mid x_i=1\}$ represents a solution of the problem w.r.t. discretization $D(P)$ of polygon $P$.
	Constraint~(\ref{eq:const-3}) enforces that any point $p_i \in D(P)$ will be visible from at least one guard from $Z$.

	In order to solve this model, we apply a general purpose solver \textsc{Cplex}~\cite{lima2010ibm}.
	\subsection{Constraint programming model} An equivalent CP model was implemented and tested by IBM ILOG CP Optimizer~\cite{}. In this case,  Constraint~(\ref{eq:const-3}) is transformed into
	\begin{equation}
	\bigvee_{ j \in V } (a_{ij} \wedge x_j) = 1,
	\end{equation}
	whereas the other constraints and the objective function are the same like in the above MIP model. Note that CP appraoch works in a branch-and-bound manner imploying a constriant propagation and variable domain filtering~\cite{laborie2018ibm}.
	\section{Algorithmic Approaches for WOAGP}
	\subsection{Greedy approaches for solving WOAGP}
	Since the WOAGP instances can be transformed into  WMSCP instances and since one of the most efficient heuristics to solve WSCP from the literature is an enhanced greedy heuristic~\cite{chvatal1979greedy}, our idea is after transforming a WOAGP instance into a WSC problem instance to	apply various greedy algorithms to solve WOAGP. Greedy algorithms produce a solution of reasonable quality within a short interval of time and are, in essence, easy to implement. Efficiency of such greedy heuristics is related to a greedy criterion utilized to expand current (non-complete, i.e., partial) solution to complete one. Among all candidates (solution components for expansion, that is not-yet-considered guards) to extend current partial solution,  we choose one with the smallest greedy value and add it to the current solution until it becomes complete (i.e., it covers all  points from $D(P)$).

	A general pseudocode of Greedy heuristics is given in Algorithm~\ref{alg:greedy}
